Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-23 paper/snakemajoranas.tex
bottom -> end

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Figure of the band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
The blue lines correspond to $\phi=0$, $B=0$ (trivial phase) and the orange lines to $\phi=\pi$, $B = \SI{1}{T}$ (topological phase).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
On the $x$-axis is the folded lattice momentum where $z_x=\SI{1300}{\nm}$.
Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=\frac{dE}{dk}$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes most insensitive to the momentum $k_x$, and thus the $v_\textrm{F}$ decreases.
As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
The parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:band_stuctures}}
% TODO: mention z_x!
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/wavefunctions}
\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi_\textrm{M}$ for (a) is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d).
The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3.5 L_x=\SI{4550}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/phasediagrams}
\caption{A comparison of a straight device (left panels) and a zigzag one (right panels).
The top panels show the Majorana wave functions, near the left edge of the system, at the value of $B_x$ for which $E_\textrm{gap}$ is maximized in a straight geometry for $\mu=\SI{10}{\meV}$ and $\phi=\pi$ as well as the values of the gap and the Majorana size.
The other panels show gap as a function of $\mu$ and $B_x$ at $\phi=\pi$ (middle panels) and as a function of $\phi$ and $B_x$ at $\mu=\SI{10}{\meV}$ (bottom panels).
The dashed lines and the dot indicate the parameters used in the other panels.
Additionally, in subplot (c) we overlay the phase boundaries.
The remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
\label{fig:phasediagrams}}
\end{figure}

>>>>

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Figure of the band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
The blue lines correspond to $\phi=0$, $B=0$ (trivial phase) and the orange lines to $\phi=\pi$, $B = \SI{1}{T}$ (topological phase).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
On the $x$-axis is the folded lattice momentum where $z_x=\SI{1300}{\nm}$.
Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=\frac{dE}{dk}$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes most insensitive to the momentum $k_x$, and thus the $v_\textrm{F}$ decreases.
As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
The parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_stuctures}}
% TODO: mention z_x!
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/wavefunctions}
\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi_\textrm{M}$ for (a) is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d).
The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3.5 L_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/phasediagrams}
\caption{A comparison of a straight device (left panels) and a zigzag one (right panels).
The top panels show the Majorana wave functions, near the left edge of the system, at the value of $B_x$ for which $E_\textrm{gap}$ is maximized in a straight geometry for $\mu=\SI{10}{\meV}$ and $\phi=\pi$ as well as the values of the gap and the Majorana size.
The other panels show gap as a function of $\mu$ and $B_x$ at $\phi=\pi$ (middle panels) and as a function of $\phi$ and $B_x$ at $\mu=\SI{10}{\meV}$ (bottom panels).
The dashed lines and the dot indicate the parameters used in the other panels.
Additionally, in subplot (c) we overlay the phase boundaries.
The remaining parameters values are written at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
\label{fig:phasediagrams}}
\end{figure}
